\documentclass[12pt,letterpaper]{article}
\title{BYLAWS} 
\author{Library Volunteer Fire Company}
\date{4-11-2023}

\usepackage{draftwatermark}
\SetWatermarkScale{5}

\begin{document}
\maketitle
\newpage
\tableofcontents
\newpage

\section{Name}
The name of this organization will be the Library Volunteer Fire Company.

\section{Purpose}
The purpose of this organization is the protection of life and property from fire hazards, accidents, and emergencies; and the maintenance, organization and equipment of the necessary apparatus and company of personnel to carry out said purpose.

\section{Membership}
Membership will be classified in two organizational areas, Corporate and Firefighting.  Any member can be classified in one or both areas.

\subsection{Corporate Membership}
Corporate Members are involved in fundraising and running the organization.  A Corporate Member must be at least 18 years of age and pass mandated background checks.  Corporate Membership will consist of the following classes: Active, Associate, Life.

\subsubsection{Active Membership}
An active member:
\begin{itemize}
\item Must attend at least one bingo per month, and one gun bash per year, and two community events per year.
\item Must attend at least six meetings per year.
\item May be eligible for any rewards program.
\item Converting from Associate Membership will not be eligible to vote in elections nor hold office for six months.
\end{itemize}

\subsubsection{Associate Membership}
An Associate Member:
\begin{itemize}
\item Must attend 2 bingos, and 1 major fundraiser per year.
\item Will not be required to attend meetings.
\item May be permitted to voice an opinion at meetings, but will not be allowed to vote.
\item Will not be eligible for any rewards program.
\item Will not be permitted to hold office.
\end{itemize}

\subsubsection{Life Membership}
Life Membership may be granted to a member with 20 years of consecutive Active Membership or 25 years of accumulated Active Membership.  Time served under Junior membership will count.  A Life Member will enjoy all the privileges of an Active Member and:
\begin{enumerate}
\item Will not be required to maintain any minimum attendance requirements for events.
\item Must attend a minimum of 2 meetings per year in order to have voting privileges.
\item Will not be required to pay dues.
\item Will be eligible to hold office per Article IV, Section 1, Subsection A.
\end{enumerate}

\subsubsection{Inactive Status}
\paragraph{Leave of Absence}
A member may request leave with the approval of membership.  Leave will not exceed 3 months for medical or personal reasons.  Leave will not exceed 6 months for educational reasons. 
\paragraph{Military Leave}
Military leave will be handled according to the Uniformed Services Employment and Reemployment Rights Act of 1994 (USERRA).

\subsection{Firefighting Membership}
Firefighting Members respond to emergency calls.  Firefighting Members will be required to meet state regulations regarding age limitations, and pass mandated background checks.  Firefighting Membership will consist of the following classes: Firefighter and Fire Support

\subsubsection{Firefighter}
A Firefighter is qualified to be an Interior Firefighter.  Firefighters must:
\begin{itemize}
\item Have successfully completed an Essentials of Firefighting Program, or provide an Essentials of Firefighting Certificate with “live burn inclusive” issued prior to 2006, or be certified at Pro Board/IFSAC Firefighter 1 level.  Equivalent certificates may be accepted at the discretion of the Fire Chief.
\item Must attend at least one drill per month or make arrangements for equivalent service at the discretion of the Fire Chief.  Exceptions to this rule are members who receive training at current career jobs.
\item Must demonstrate continued proficiency in job performance requirements.
\end{itemize}

\subsubsection{Fire Support}
Fire support consists off all fireground and emergency response positions that do not have the requirements of Firefighter, such as Exterior Firefighter, Fire Police, and other positions as deemed necessary by the Fire Chief.  Qualifications for each position shall be determined by the Fire Chief.  Fire support must:
\begin{itemize}
\item Attend at least one drill per month or make arrangements for equivalent service at the discretion of the Fire Chief.
*\item Must demonstrate continued proficiency in job performance requirements.
*\item Juniors must operate within the guidelines of the State of Pennsylvania “Junior Emergency Services Compliance Manual” and Company Operating Guidelines.
\end{itemize}

\subsubsection{Junior Membership}
Juniors  are minors who wish to participate in fire support.  Juniors:
\begin{itemize}
\item Fall under the discretion and direction of the Fire Chief.
\item Must be 14 to 17 years old.
\item Must maintain a 2.0 Grade Point Average.
\item May attend meetings and have a voice, but not a vote.
\end{itemize}
Junior members, upon reaching the age of 18, and applying for Active Membership, may have their service time applied to their 6 month probationary period, or portions thereof, at the approval of the membership.

\subsection{Probation}
The probationary period will be six months.  A probationary Member shall not be eligible for elective office for a period of one year from the date of application.
Probationary Members may:
\begin{itemize}
\item Voice an opinion at a meeting.
\item Serve on a committee and have a voice and a vote on that committee.
\end{itemize}
Probationary Members may not: 
\begin{itemize}
\item Vote on any issue at any regular meeting or special meeting.
\item Enter or remain in any Fire Company building without the presence of an active member, unless authorized by the Fire Chief, President, or Chairman of the Board. 
\item Display any fire company insignia, such as A/B uniforms, vehicle plates, badges, etc., with the exception of firefighting equipment, PPE, or LVFC shirts while attending fire classes or functions.
\end{itemize}

\subsection{Delinquent Status}
At each membership meeting, it shall be reported if any members are delinquent in their Active membership obligations.  The member will be notified.  If they are not caught up by the next membership meeting, they will be put on delinquent status for 3 months.  A member that continues to be delinquent for 3 months will be removed from membership.  A member that becomes delinquent loses their rewards for the year.

\subsection{Resignation or Removal}
Members wishing to resign must submit a written resignation to the Membership Committee.  Members are permitted to rescind their resignation in writing within 30 days.  Members may also be removed for cause.  All equipment belonging to the fire department must be returned at the time of membership termination.  Former members returning to the organization must undergo New Member Admission processes as a new member.  Any former members removed for disciplinary reasons will not be eligible to return for 1 year.

\subsection{Dues}
Dues of \$10 shall be collected annually at or prior to the December membership meeting.

\subsection{Social Hall Privileges}
Any currently Active Member, after being an Active Member for one year and in good standing, and with Board approval, will be entitled to use the Social Hall for themselves, their spouses, or their immediate family, consisting of parents, their children, brothers, or sisters.

\section{Officers}

\subsection{Corporate Officers}
The Corporate officers shall consist of the President, Vice President, Recording Secretary, Treasurer, Financial Secretary, 3 Directors and the Fire Chief.  These officers shall perform the duties prescribed by these bylaws.

\subsubsection{Qualifications}
All corporate officers must have been a current, active member for three years.  Life members qualify for all offices, but must maintain meeting attendance requirements under Active Membership during the term.  The Fire Chief has additional qualifications listed under Fire Officers.

\subsubsection{Duties}
\paragraph{President}
The President shall represent the Library Volunteer Fire Company.  The President shall sign contracts, checks, and documents of this nature when authorized by the Membership and jointly with the Treasurer. The President, within 30 days of assuming the office, shall give bond, in an amount to be determined each fiscal year, to the Chairman of the Board.
\paragraph{Vice President}
The Vice President shall perform, in the absence of the President, all duties of the President.  If specifically delegated by the President or the Board of Directors, the Vice President may have the power to sign checks with the Treasurer.  In the event of a Vice President filling the vacancy of the President, the Chairman of the Board shall assume the duties of the Vice President until the next meeting where an election will be held for a new Vice President.
\paragraph{Recording Secretary}
The Recording Secretary shall complete the minutes within seven days of meetings. The minutes shall not leave the premises.  Any information pertaining to matters discussed and/or decided at any meeting shall not be released to non-members without the approval of the President, Chairman of the Board, and Fire Chief.
\paragraph{Treasurer}
The Treasurer shall pay out the funds of the Fire Company.  The Treasurer shall arrange for an independent audit by a certified public accountant to take place before any federal filing date(s), if any. The results of the audit shall be reported to the Membership within a reasonable time of its completion. The Treasurer, within 30 days of assuming the office, shall give bond, in an amount to be determined each fiscal year, to the Chairman of the Board.
\paragraph{Financial Secretary}
The Financial Secretary will assist the Treasurer in payments, maintaining an account of all funds received and all orders paid, and preparing the monthly financial statements.  The Financial Secretary, in cooperation with the fundraising committees, will be responsible for the coordination of the annual fund drives and tracking all monies received.  The Financial Secretary will be responsible for establishing a yearly operating budget to be presented prior to the annual meeting.  The Financial Secretary will be responsible for filing of tax returns.
\paragraph{Directors}
There shall be 3 Directors.
\paragraph{Fire Chief}
The Fire Chief is considered a corporate and fire officer.  Fire Chief duties are prescribed under Fire Officers.

\subsection{Fire Officers}
The Fire Officers may consist of a Chief, Assistant Chief, two Deputy Chiefs, one Captain, and two Lieutenants.  Positions may remain vacant if desired by the Fire Chief and agreed upon by membership.  The Chief and Assistant Chief is elected.  The Fire Chief will submit his appointments for Deputy Chiefs, Captain, and Lieutenants to the President and Chairman of the Board within 7 days of elections.  Any disagreements on appointments will be handled by membership at a special meeting.

\subsubsection{Qualifications}
All officers must be Active Members, be certified to drive and pump all apparatus per department SOP/SOG.  Unless otherwise specified, all officers must live in South Park Township or within 3 nautical miles of the fire hall.
\begin{itemize}
\item A Fire Chief must be certified at Fire Officer 1, be a resident of South Park Township, and have been an interior firefighter at LVFC for 5 years.
\item An Assistant Chief must be certified at Firefighter II, be a resident of South Park Township, and have been an interior firefighter at LVFC for 4 years.
\item A Deputy Chief must be certified at Firefighter I and have been an interior firefighter at LVFC for 3 years.
\item A Captain must be certified at Firefighter I and have been an interior firefighter at LVFC for 2 years.
\item A Lieutenant must be an interior firefighter and have been an interior firefighter at LVFC for 1 year.
\end{itemize}

All officers must attend at least 16 hours of certificate training per year, that are not part of weekly drills.

Qualifications for any office may be suspended by 2/3 vote.

\subsubsection{Duties}
\paragraph{Fire Chief}
The Fire Chief shall take command of the Fire Company and equipment, at the engine house, during any response, and at every fire alarm or emergency. The Fire Chief shall ensure that all fire, rescue, emergency equipment, and apparatus are kept in good condition and ready for use at all times. The Fire Chief shall be responsible to ensure and/or assign qualified drivers to each vehicle. The Fire Chief shall have complete control in assignment of home monitors and shall have tests conducted in an alarm and dispatch system(s) when necessary. The Fire Chief shall be ex-officio of the Board of Directors, but shall have no vote. The Fire Chief, throughout his term, shall have use of a fire company vehicle as long as there is one available for such use. In the event that the Fire Chief is out of service, the next available Line Officer shall have access to the Fire Chief’s vehicle. The Fire Chief shall be responsible to ensure the Company Officers and firefighters receive sufficient and appropriate training, drills, skills, and experiences. The Fire Chief shall be responsible to ensure sufficient operational safety systems and practices are used at all incidents and responses. The Chief shall be responsible for setting forth the criteria necessary to a) be an emergency vehicle driver, b) to use SCBA and be an interior firefighter, and c) to be a Safety Officer.
\paragraph{Assistant Chief}
It shall be the duty of the Assistant Chief, in the absence of the Fire Chief, to perform all of the duties pertaining to the office of Fire Chief
\paragraph{Line Officers}
Line officers shall consist of two Deputy Chiefs, a Captain, and two Lieutenants.  Line Officer’s duties will be outlined in Fire Department SOGs.

\subsubsection{Vacancies}
In the case of a vacancy in the office of the Fire Chief, the next highest ranking officer will become the Acting Fire Chief until the next monthly meeting where a few Fire Chief will be elected.

\subsection{Nominations}
The month prior to the Annual Meeting, nominations will be taken from the floor.

\subsection{Elections}
The elections will be held by ballot vote at the Annual Meeting.  Only Active and Life Members can vote for Corporate Officers.  Only Firefighters and Fire Support can vote for Assistant Chief.  The Fire Chief is voted on by Active, Life Members, Firefighters, and Fire Support.

\subsection{Terms of Office}
The President will serve 2 year terms being elected in even years and until a successor is elected.  The Fire Chief will serve 2 year terms being elected in odd years and until a successor is elected.  The Chairman of the Board will serve a one year term and remain as a Director the following term.   All other offices will have a one year term and until a successor is elected.  Terms of office will start at the close of the Annual Meeting.

\subsection{Limitations}
A member can have a corporate office and fire office, but cannot hold more than one of each.  The Fire Chief is limited to that single office.  

Check signers cannot be related or be domestic partners.

\section{Meetings}

\subsection{Regular Meetings}
The regular monthly meeting shall be held the day after the South Park Board of Supervisors meeting, or otherwise upon proper notice. 

\subsection{Annual Meeting}
The Regular Meeting in November shall be known as the Annual Meeting when elections will be held in addition to normal business.

\subsection{Special Meetings}
The President or Board may call for a special meeting.  A special meeting must be called if a written request, signed by seven active members in good standing, is submitted.  Members shall be notified by telephone or word of mouth at least one day prior to any special meeting, and a notice shall be posted at the station.

\subsection{Quorum}
Seven active members shall constitute a quorum.

\section{Executive Board}

\subsection{Board Composition}
The Corporate Officers, including Directors, shall constitute the Executive Board.  The President and the Fire Chief shall have a voice but no vote.

\subsection{Chairman of the Board}
The Chairman of the Board is a Director elected by fellow Board Members.  The Chairman is authorized to sign any contract approved by the Membership. 

\subsection{Qualifications for Chairman of the Board}
The Chairman must have been a Director for at least one year.

\subsection{Board's Duties and Powers}
The Board shall have charge of all properties of the Fire Company.
\begin{itemize}
\item Review all applications of charitable or non-profit organizations that wish to rent the social hall and make a final decision on each applicant. 
\item Have access to all Fire Company equipment, documents, database, and/or property at anytime and cause an audit the books of the Fire Company at the beginning of each year. 
\item Have the power to spend up to \$3,000 for repairs, replacements, or improvements, of an urgent nature without prior approval.  The Board’s actions may be reversed by membership.
\item Review all insurance policies, coverages and limits (including any Fire Company supplemented insurances, Fidelity Bonds, liability coverages and limits, fire and casualty coverage, etc.). 
\end{itemize}

\subsection{Board Meetings}
Unless otherwise ordered, all meetings of the Board will be held the Sunday prior to the South Park Board of Supervisors meeting.  A majority of the Board shall constitute a quorum. 

\subsection{Attendance Requirements}
A Director missing two consecutive Board meetings without just cause may be dropped from the board and a new Director elected at the next regular membership meeting.  

\section{Committees}

\subsection{Committees, in general}
Committees are to be appointed by the Executive Board, with the exception of the Truck Committee.  The President and Chairman of the Board are to be ex-officio members of all Committees.

\subsection{Standing Committees}
The Standing Committees are: 
\begin{itemize}
\item Bingo 
\item Fundraising 
\item By-Laws 
\item Awards
\item Membership
\item Open House 
\item Hall Rental 
\item Kitchen 
\item Flowers
\item Rewards
\end{itemize}

\subsection{Interim Committees}
Any interim committees are created and appointed as needed by the Board of Directors.

\subsection{Membership Committee}
The Membership Committee shall consist of the Executive Board, and two appointed Members. The Membership Committee shall make a list of Members eligible to vote and hold office in the Fire Company and to act as the Hearing Board.

\subsection{Truck Committee}
The Fire Chief shall appoint a Truck Committee when the need arises.

\section{Disciplinary Proceedings}
Charges must be submitted to the Board for initial investigation within 15 days of the violation.  If found to be valid, the Board will refer the matter to the Membership Committee or select a special committee for trial.

\section{Parliamentary Authority}
The rules contained in the current edition of Robert's Rules of Order Newly Revised shall govern the organization in all cases to which they are applicable and in which they are not inconsistent with these bylaws and any special rules of order the organization may adopt.

\section{Amendment of Bylaws}
The members may amended these bylaws by submitting a change in writing, reading the changes at two meetings, and passing with two-thirds vote at a third meeting.

\section{Miscellaneous}

\subsection{Non-Profit Use of Social Hall}
Non-profit organizations may request permission to use the Social Hall by notifying the Board of Directors.  The Board will handle the approval process and handle further business with the non-profit.
\subsection{Priority of Fire Company Business}
Fire Company business shall supersede all requests for use of the Social Hall unless this would cause a breach of contract.  States of Emergencies supersede all requests and contracts.

\subsection{Checks Require Two Signatures}
The funds of the Fire Company can be paid with checks signed by two people.  One of the signatures must be the Treasurer or Financial Secretary.  The other signature must be the President or Vice President.


\section{Revision History}
\begin{itemize}
\item 2018 Major Revision by Bylaws Committee: Robert Craig, Larry Daberko, Ted Hale, Jr., Bruce Rayner, Steve West.
\item 2019 Revisions by Board of Directors
\item 2019-12-10 – Adopted by membership.
\item 2021-01-12 – Change recording secretary qualification from 1 year to 3 years membership.
\item 2021-08-10 – Permit suspension of qualifications of fire officers by 2/3 vote.
\item 2021-08-10 – Remove fire chief from full discretion of use for command vehicle.
\item 2022-07-12 – Add check signing restriction.
\item 2022-07-12 – Change Fireground Support drill requirements.
\item 2022-07-12 – Clarify Fire Officer membership qualifications.
\item 2023-04-11 – Change Associate Member requirements.
\end{itemize}

\end{document}

